A large-scale analysis of racial disparities in police stops across the

### 2019-07-16 lib/paper_results.Rmd
progress

We have collected and released a dataset of 
`r pfs$basic_counts$collected$n_stops` traffic stops carried out by 
`r pfs$basic_counts$collected$n_states` state patrol agencies and 
`r pfs$basic_counts$collectec$n_cities` municipal police departments.

We analyzed a unique dataset detailing 
`r pfs$basic_counts$analyzed$n_stops` traffic stops carried out by 
`r pfs$basic_counts$analyzed$n_states` state patrol agencies and 
`r pfs$basic_counts$analyzed$n_cities` municipal police departments.

@@

```{r stop_rates}
pfs$stop_rates %>% 
  filter(subject_race %in% c("black", "white", "hispanic")) %>% 
  kable()
```

```{r search_rates}
pfs$search_rates %>% 
  filter(subject_race %in% c("black", "white", "hispanic")) %>% 
  kable()
```

>>>>

We have collected and released a dataset of 
`r pfs$counts$collected$n_stops` traffic stops carried out by 
`r pfs$counts$collected$n_states` state patrol agencies and 
`r pfs$counts$collectec$n_cities` municipal police departments.

We analyzed a unique dataset detailing 
`r pfs$counts$analyzed$n_stops` traffic stops carried out by 
`r pfs$counts$analyzed$n_states` state patrol agencies and 
`r pfs$counts$analyzed$n_cities` municipal police departments.

@@

```{r stop_rates}
pfs$plots$stop
pfs$rates$stop %>% 
  group_by(subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate))
  kable()
```

```{r search_rates}
pfs$plots$search
pfs$rates$search %>% 
  group_by(subject_race) %>%
  summarize(average_search_rate = mean(search_rate))
  kable()
```
